Data Visualisation in R

### 2023-11-01 inst/tutorials/MSc_Data_Vis/MSc_Data_Vis.Rmd
space
fixed spacing issue?

```{r Ex3test, exercise = T}
library(palmerpenguins)

# histogram
hist(penguins$flipper_length_mm)

# plot
plot(flipper_length_mm ~ bill_length_mm, data = penguins)

# boxplot
boxplot(flipper_length_mm ~ species, data = penguins)

>>>>

```{r Ex3test, exercise = T}
library(palmerpenguins)
# histogram
hist(penguins$flipper_length_mm)
# plot
plot(flipper_length_mm ~ bill_length_mm, data = penguins)
# boxplot
boxplot(flipper_length_mm ~ species, data = penguins)
```
